Identity Blockchain - Proof of Identity

### 2022-07-23 paper.tex
registerKp using verifyProof

\hfill\begin{minipage}{\dimexpr\textwidth-20px}
\begin{lstlisting}[language=Solidity]
  mapping(uint256 => uint256) public ninKidKpUsed;
  mapping(uint256 => bool) public kpInvalid;
  mapping(uint256 => uint256) public ninKidKpLastConfirmed;

  function registerKp(
    uint256 ninKid,
    uint256 ninKidKp,
    bytes proof
  ) public {
    uint256 previousKey = ninKidKpUsed[ninKid];
    if (previousKey == ninKid) return; // already registered
    bool ok = zksnarkverify(VK, [ninKid, ninKidKp], proof); // VK = verification key
    if (ok && !kpInvalid[ninKidKp]) {
      if (previousKey != 0) kpInvalid[previousKey] = true;
      ninKidKpUsed[ninKid] = ninKidKp;
      ninKidKpLastConfirmed[ninKid] = block.number;
    }
  }
\end{lstlisting}
\xdef\tpd{\the\prevdepth}
\end{minipage}
\item[] \underline{Features}
\begin{itemize}
      \item[] \textbf{Sybil resistance} \\ $\khk$ is a unique public key bound to the Person on the \pbc{}. By design, the Person cannot have two valid $\khk$ keys at the same time.

>>>>

\hfill\begin{minipage}{\dimexpr\textwidth-20px}
\begin{lstlisting}[language=Solidity]
  mapping(uint => uint) public ninKidKpUsed;

  function registerKp(
    uint hNinKid,
    uint hNinKidKp,
		uint[2] memory proofPointA,
		uint[2][2] memory proofPointsB,
		uint[2] memory proofPointC
  ) public {

		//Setting public arguments
		uint[] memory inputValues = new uint[](2)
		inputValues[0] = hNinKid;
		inputValues[1] = hNinKidKp;

		require(
			verifyProof(
				proofPointA,
				proofPointsB,
				proofPointC,
				inputValues
			)
		);

    ninKidKpUsed[hNinKid] = hNinKidKp;
  }
\end{lstlisting}
\xdef\tpd{\the\prevdepth}
\end{minipage}
\item[] \underline{Features}
\begin{itemize}
      \item[] \textbf{Sybil resistance} \\ $\khk$ is a unique public key bound to the Person on the \pbc{}. By design, the Person cannot have two valid $\khk$ keys at the same time.
